Open-source landscape for 3D CSEM modelling

### 2020-09-02 manuscript/Manuscript.tex

\simpeg interfaces to various solvers including \texttt{PARDISO} \citep{FGCS.04.Schenk}, \texttt{MUMPS} \citep{SIAM.01.Amestoy}, as well as those implemented in the \texttt{scipy.sparse.linalg} module \citep{NM.20.Virtanen}. For problems with many sources (and reciprocity is not a natural solution, e.g. in 3D airborne EM), \simpeg contains machinery for domain-decomposition approaches; see for example \cite{GEO.20.Fournier}.

>>>>

\simpeg interfaces to various solvers including \texttt{PARDISO} \citep{FGCS.04.Schenk}, \texttt{MUMPS} \citep{SIAM.01.Amestoy}, as well as those implemented in the \texttt{scipy.sparse.linalg} module \citep{NM.20.Virtanen}. For problems with many sources (e.g. airborne EM), \simpeg contains machinery for domain-decomposition approaches; see for example \cite{GEO.20.Fournier}.
